---
title: "ESM 206 Lab 8"
author: "Claire Gonzales"
date: "11/15/2021"
output: html_document
---

```{r setup, include=FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

# Attach packages
library(tidyverse)
library(here)
library(corrplot)
library(stargazer)
library(broom)
library(modelsummary)
```

## Read in Data

```{r}
homes <- read_csv(here("data", "slo_homes.csv"))
```

A little bit of cleaning:

Make a subset called homes_sub that only contains observations where the city is:

- San Luis Obispo
- Arroyo Grande
- Atascadero
- Santa Maria-Orcutt

```{r}
homes_sub <- homes %>% 
  filter(City %in% c("San Luis Obispo", "Arroyo Grande", "Atascadero", "Santa Maria-Orcutt"))
```

## Do a little exploring of our data

Summary statistics (home price, based on city and sale status):
- Find and return in a nice summary table the mean and standard deviation of home price, grouped by city and sale status.

```{r, include=FALSE, eval=FALSE}
homes_summary <- homes_sub %>% 
  group_by(City, Status) %>% 
  summarize(
    Mean = round(mean(Price, na.rm = TRUE), 2),
    SD = round(sd(Price, na.rm = TRUE), 2))
  )

# Dont even want to run this code? eval = FALSE in set up line of that code chunk

ggplot(data = homes_sub, aes(x = Price)) +
  geom_density(aes(color = City, fill = City), alpha = 0.3) +
  scale_x_continuous(limits = c(0,3e6))
```

Explore the visual relationship between square footage and home price

```{r}
ggplot(data = homes_sub, aes(x = SqFt, y = Price)) +
  geom_point(aes(color = City, shape = Status), alpha = 0.4) +
  geom_smooth(method = lm) +
  scale_y_continuous(limits = c(0,3e6))
```

## Model the relationship with home price as dependent variable (DV)

```{r}

homes_lm1 <- lm(Price ~ City + Bedrooms + Bathrooms + SqFt + PricePerSqFt + Status, data = homes_sub)

# Make a subset that only contains the quantitative variables 

homes_quant <- homes_sub %>% 
  select(Price:PricePerSqFt)

homes_cor <- cor(homes_quant)
homes_cor

corrplot(homes_cor)

# how would i explore diagnostic plots for lm1?

plot(homes_lm1)
```

Try another model where we simplify this a bit:

- city
- sqft
- status

```{r}
homes_lm2 <- lm(Price ~ City + SqFt + Status, data = homes_sub)
homes_lm2

plot(homes_lm2)


# but we should consider best fit as well 

summary(homes_lm1)
summary(homes_lm2)
```

Find the AIC value of each model:

```{r}
AIC(homes_lm1)
AIC(homes_lm2)

# there is a huge gap here in the model fit values. So maybe there is an intermediate model that would be best
```

Find an intermediate model that might make most sense:

```{r}
homes_lm3 <- lm(Price ~ City + SqFt + Status + Bathrooms, data = homes_sub)
homes_lm3

plot(homes_lm3)

summary(homes_lm3)

AIC(homes_lm3)
```

Use model summary to show model outputs side-by-side:
BUT if you use modelsummary to  return outputs of multiple models, it wants you to feed it to it as list.
```{r}
modelsummary(homes_lm1)
modelsummary(list(homes_lm1, homes_lm2, homes_lm3))
```

## start making predictions with this model

Use `broom::augment`

```{r}
homes_predicted <- augment(homes_lm1)
```

Use the `predict()` function to try out your model on new scenarios that you create. 

# MY COOL UPDATE