---
title: "ESM206_Lab 8"
author: "Claire Gonzales"
date: "11/15/2021"
output: html_document
---

```{r setup, include=FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

# Attach packages
library(tidyverse)
library(here)
library(corrplot)
library(stargazer)
library(broom)
library(modelsummary)
```

## Read in Data

```{r}
homes <- read_csv(here("data", "slo_homes.csv"))
```

A little bit of cleaning:

Make a subset called homes_sub that only contains observations where the city is:

- San Luis Obispo
- Arroyo Grande
- Atascadero
- Santa Maria-Orcutt

```{r}
homes_sub <- homes %>% 
  filter(City %in% c("San Luis Obispo", "Arroyo Grande", "Atascadero", "Santa Maria-Orcutt"))
```

## Do a little exploring of our data

Summary statistics (home price, based on city and sale status):
- Find and return in a nice summary table the mean and standard deviation of home price, grouped by city and sale status.

```{r, include=FALSE, eval=FALSE}
homes_summary <- homes_sub %>% 
  group_by(City, Status) %>% 
  summarize(
    Mean = round(mean(Price, na.rm = TRUE), 2),
    SD = round(sd(Price, na.rm = TRUE), 2))
  )

# Dont even want to run this code? eval = FALSE in set up line of that code chunk

ggplot(data = homes_sub, aes(x = Price)) +
  geom_density(aes(color = City, fill = City), alpha = 0.3) +
  scale_x_continuous(limits = c(0,3e6))
```

Explore the visual relationship between square footage and home price

```{r}
ggplot(data = homes_sub, aes(x = SqFt, y = Price)) +
  geom_point(aes(color = City, shape = Status), alpha = 0.4) +
  geom_smooth(method = lm) +
  scale_y_continuous(limits = c(0,3e6))
```

